Fast Bayesian Inference for Exoplanet Discovery in Radial Velocity Data

### 2014-10-19 Paper/ms.tex
Gliese 581 figures
Abstract tweaks

\begin{abstract}
Inferring the number of planets $N$ in an exoplanetary system from radial velocity
(RV) data is a challenging task. Typically, the posterior distribution for the
planet parameters is multimodal and may have other awkward features. In
addition, when $N$ is unknown, the marginal likelihood (or evidence), as a
function of $N$, is required. In this paper we propose an alternative
approach using a trans-dimensional Markov Chain Monte Carlo method within
Nested Sampling. We also implement the likelihood function using a look-up
table of pre-computed elliptical orbits.
The posterior distribution for $N$ can be obtained with a
single run, which takes $\sim$ 10 minutes on a typical modern desktop computer.
We apply the method to $\nu$ Oph and XXX, and find moderate evidence
(posterior probability of existence = 70\%) for a third planet around
$\nu$ Oph with an orbital period of 75.7 $\pm$ 1.8 days.
\end{abstract}

@@

>>>>

\begin{abstract}
Inferring the number of planets $N$ in an exoplanetary system from radial velocity
(RV) data is a challenging task. Typically, the posterior distribution for the
planet parameters is multimodal and may have other awkward features. In
addition, when $N$ is unknown, the marginal likelihood (or evidence), as a
function of $N$, is required. In this paper we propose an alternative
approach using a trans-dimensional Markov Chain Monte Carlo method within
Nested Sampling. The posterior distribution for $N$ can be obtained with a
single run, which takes $\sim$ 15 minutes on a typical modern desktop computer.
We apply the method to $\nu$ Oph and Gliese 581, finding moderate evidence
(posterior probability of existence = 70\%) for a third planet around
$\nu$ Oph with an orbital period of 75.7 $\pm$ 1.8 days. 
\end{abstract}

@@

\begin{figure}
\includegraphics[scale=0.5]{Figures/gliese581_N.eps}
\caption{The posterior distribution for the number of planets $N$ orbiting
Gliese 581.\label{fig:gliese581_N}}
\end{figure}

\begin{figure}
\includegraphics[scale=0.5]{Figures/gliese581_periods.eps}
\caption{The posterior distribution for the orbital periods in the Gliese 581
system.\label{fig:gliese581_periods}}
\end{figure}
